Model Checking

### 2024-03-06 owen/Write Ups/04_model_checking.qmd
tidying up these models

The aim of this document is to summarise the current version 
of the model and describe some of the ways we have assessed the
suitability of this model to our data. The
aim is for this document to be self contained.

@@

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 8)

@@

We fit this to games from all players in the 1700-1900 range. 
We looked only at standard rated bullet games (no tournaments, etc),
which 675k games, ranging from 500 - 128k games per player.
Fitting this model takes many hours on a computing cluster.

@@

```{r}
fit <- readRDS(here("results/", "Full_Fits", "lichess1700-1900/", 
                    "all_rated_bullet_model.RDS"))

@@

mcmc_hist(fit$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")

@@

```{r winner-effects-17-19}
#| fig.height = 9

@@

mcmc_hist(fit$draws("beta"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Player Winner Effects")
```

@@

```{r indiv-effects-17-19}
#| fig.height = 6

names(players) <- paste0("alpha[", 1:length(users), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit$draws("alpha"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Individual Player Effects")
```

@@

TO BE COMPLETED

@@

```{r}
#| eval: false

@@

mcmc_hist(fit2$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")

@@

```{r}
#| eval: false

@@

mcmc_hist(fit2$draws("beta"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Player Winner Effects")

@@

```{r}
#| eval: false

names(players) <- paste0("alpha[", 1:length(users_20_22), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit2$draws("alpha"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Individual Player Effects")
```

@@

```{r}
fit3 <- readRDS(here("results/", "Full_Fits", "lichess2300-2500/", 
                    "all_rated_bullet_model.RDS"))

@@

mcmc_hist(fit3$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")
```

```{r}

@@

mcmc_hist(fit3$draws("beta"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Player Winner Effects")

@@

```{r}
names(players) <- paste0("alpha[", 1:length(users_23_25), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit3$draws("alpha"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Individual Player Effects")
```

@@

```{r}

fit <- readRDS(here("results/", "Full_Fits", "lichess1700-1900/", 
                    "all_rated_blitz_model.RDS"))

mcmc_hist(fit$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")

@@

mcmc_hist(fit$draws("beta"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Player Winner Effects")

## indiv effects
names(players) <- paste0("alpha[", 1:length(users), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit$draws("alpha"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Individual Player Effects")
```

@@

TO BE COMPLETED

```{r}
#| eval: false

fit2 <- readRDS(here("results/", "Full_Fits", "lichess2000-2200/", 
                    "all_rated_blitz_model.RDS"))

mcmc_hist(fit$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")

@@

mcmc_hist(fit2$draws("delta"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Player Winner Effects")

## indiv effects
names(players) <- paste0("alpha[", 1:length(users), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit2$draws("alpha"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Individual Player Effects")

@@

@@

TO BE COMPLETED

```{r}
#| eval: false

fit3 <- readRDS(here("results/", "Full_Fits", "lichess2300-2500/", 
                    "all_rated_blitz_model.RDS"))

@@

@@

```{r}

fit <- readRDS(here("results/", "Full_Fits", "lichess1700-1900/", 
                    "all_rated_bullet_model_prev.RDS"))

mcmc_hist(fit$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")

@@

mcmc_hist(fit$draws("delta"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Player Winner Effects")

## indiv effects
names(players) <- paste0("alpha[", 1:length(users), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit$draws("alpha"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Individual Player Effects")
```

@@

```{r}
fit2 <- readRDS(here("results/", "Full_Fits", "lichess2000-2200/", 
                    "all_rated_bullet_model_prev.RDS"))

mcmc_hist(fit$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")

@@

mcmc_hist(fit2$draws("delta"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Player Winner Effects")

## indiv effects
names(players) <- paste0("alpha[", 1:length(users_20_22), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit2$draws("alpha"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Individual Player Effects")
```

@@

```{r}
fit3 <- readRDS(here("results/", "Full_Fits", "lichess2300-2500/", 
                    "all_rated_bullet_model_prev.RDS"))

mcmc_hist(fit3$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")

fit3$summary(variables = c("mu1", "mu2", "gamma1", "gamma2"))

@@

mcmc_hist(fit3$draws("delta"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Player Winner Effects")

## indiv effects
names(players) <- paste0("alpha[", 1:length(users_23_25), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit3$draws("alpha"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Individual Player Effects")
```

### 1700-1900 Blitz

```{r}
fit <- readRDS(here("results/", "Full_Fits", "lichess1700-1900/", 
                    "all_rated_blitz_model_prev.RDS"))

mcmc_hist(fit$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")

mcmc_hist(fit$draws("delta"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Player Winner Effects")

## indiv effects
names(players) <- paste0("alpha[", 1:length(users), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit$draws("alpha"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Individual Player Effects")
```

### 2000-2200 Blitz

```{r}
fit2 <- readRDS(here("results/", "Full_Fits", "lichess2000-2200/", 
                    "all_rated_blitz_model_prev.RDS"))

mcmc_hist(fit2$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")

mcmc_hist(fit2$draws("delta"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Player Winner Effects")

## indiv effects
names(players) <- paste0("alpha[", 1:length(users_20_22), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit2$draws("alpha"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Individual Player Effects")
```

### 2300-2500 Blitz

```{r}
fit3 <- readRDS(here("results/", "Full_Fits", "lichess2300-2500/", 
                    "all_rated_blitz_model_prev.RDS"))

mcmc_hist(fit3$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")

fit3$summary(variables = c("mu1", "mu2", "gamma1", "gamma2"))

mcmc_hist(fit3$draws("delta"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Player Winner Effects")

## indiv effects
names(players) <- paste0("alpha[", 1:length(users_23_25), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit3$draws("alpha"),
          facet_args = list(labeller = player_labels)) +
  labs(title = "Individual Player Effects")
```

@@

```{r}
## load in the data for this

@@

```{r}
## look at different bin
path_id <- 1
data_path <- all_data_path[path_id]
files <- list.files(data_path)

@@

small_data_1 <- lichess_data %>%
  # filter(Event == "Rated Bullet game") %>%
  # filter(TimeControl == "60+0") %>%
  filter(Variant == "Standard") %>%
  filter(grepl("Rated Bullet game", Event))

users_1 <- unique(small_data_1$Username)

small_data_1$dttm <- as.POSIXct(paste(small_data_1$UTCDate,
                                      small_data_1$UTCTime),
                              format="%Y-%m-%d %H:%M:%S", tz = "UTC")

small_data_1 %>% 
  mutate(UserELO = ifelse(Username == White, WhiteElo, BlackElo)) %>% 
  group_by(Username) %>% 
  arrange(UTCDate, UTCTime, .by_group = TRUE) %>% 
  select(Username, dttm, UserELO) %>% 
  filter(Username %in% users_1[1:16]) %>% 
  # slice_sample(n = 100) %>% 
  ggplot(aes(dttm, UserELO, colour = as.factor(Username))) +
  geom_line() +
  labs(colour = "User", x = "Date") +
  geom_hline(yintercept = c(1700, 1900), 
             col = "red", linetype = "dashed", alpha = 0.5) +
  facet_wrap(~Username, scales = "free")
```

@@

## Old Questions

Do focal players play each other in this data?

```{r}
data_path <- here("box_data/lichess1700-1900/")

files <- list.files(data_path)
files <- files[1:25]

users <- unique(lichess_data$Username)

overlap_data <- lichess_data %>% 
  filter(White %in% users & Black %in% users) %>% 
  filter(Variant == "Standard") %>% 
  filter(grepl("Rated Bullet game", Event))

rm(lichess_data)

overlap_data %>% group_by(Username) %>% 
  tally() %>% 
  arrange(-n)
```

Certain players have a large amount of overlap, looking only at the games we
consider in the analysis. How should these games be accounted for?

```{r check for 2000-2200 games also}
#| eval: false

## happens here also, but not as often for this sample

data_path <- here("box_data/lichess2000-2200/")

files <- list.files(data_path)
files <- files[1:10]

users <- unique(lichess_data$Username)

overlap_data <- lichess_data %>% 
  filter(White %in% users & Black %in% users) %>% 
  filter(Variant == "Standard") %>% 
  filter(grepl("Rated Bullet game", Event))

rm(lichess_data)

overlap_data %>% group_by(Username) %>% 
  tally() %>% 
  arrange(-n)

>>>>

The aim of this document is to summarise the current version 
of the model and describe some of the ways we have assessed the
suitability of this model to our data. This document should be self contained.

@@

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 8, dev = "png",
                      fig.height = 5, dpi = 200)

@@

We fit this to games from all players in the 1700-1900 range. 
We looked only at standard rated bullet games (no tournaments, etc),
which was 675k games, ranging from 500 - 128k games per player.
Fitting this model takes many hours on a computing cluster.

@@

```{r 17-19-bullet-global, fig.path = "figures/"}
fit <- readRDS(here("results/", "Full_Fits", "lichess1700-1900/", 
                    "all_rated_bullet_model.RDS"))

@@

mcmc_hist(fit$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters 17-19 Bullet",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")

@@

```{r winner-effects-17-19-bullet, fig.path = "figures/"}
#| fig-height: 9

@@

mcmc_hist(fit$draws("beta"),
          facet_args = list(labeller = player_labels, ncol = 5)) +
  labs(title = "Player Winner Effects 17-19 Bullet")
```

@@

```{r indiv-effects-17-19-bullet, fig.path = "figures/"}
#| fig-height: 9

names(players) <- paste0("alpha[", 1:length(users), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit$draws("alpha"),
          facet_args = list(labeller = player_labels, ncol = 5)) +
  labs(title = "Individual Player Effects 17-19 Bullet")
```

@@

@@

```{r global-effects-20-22-bullet, fig.path = "figures/"}

@@

mcmc_hist(fit2$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters 20-22 Bullet",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")

@@

```{r winner-effects-20-22-bullet, fig.path = "figures/"}
#| fig-height: 9

@@

mcmc_hist(fit2$draws("beta"),
          facet_args = list(labeller = player_labels, ncol = 5)) +
  labs(title = "Player Winner Effects 20-22 Bullet")

@@

```{r indiv-effects-20-22-bullet, fig.path = "figures/"}
#| fig-height: 9

names(players) <- paste0("alpha[", 1:length(users_20_22), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit2$draws("alpha"),
          facet_args = list(labeller = player_labels, ncol = 5)) +
  labs(title = "Individual Player Effects, 20-22 Bullet")
```

@@

```{r global-effects-23-25-bullet, fig.path = "figures/"}
fit3 <- readRDS(here("results/", "Full_Fits", "lichess2300-2500/", 
                    "all_rated_bullet_model.RDS"))

@@

mcmc_hist(fit3$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters 23-25 Bullet",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")

fit3$summary(variables = c("mu1", "mu2", "gamma1", "gamma2"))
```

```{r winner-effects-23-25-bullet, fig.path = "figures/"}
#| fig-height: 9

@@

mcmc_hist(fit3$draws("beta"),
          facet_args = list(labeller = player_labels, ncol = 5)) +
  labs(title = "Player Winner Effects 23-25 Bullet")

@@

```{r indiv-effects-23-25-bullet, fig.path = "figures/"}
#| fig-height: 9

names(players) <- paste0("alpha[", 1:length(users_23_25), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit3$draws("alpha"),
          facet_args = list(labeller = player_labels, ncol = 5)) +
  labs(title = "Individual Player Effects 23-25 Bullet")
```

@@

Note that now there are 187k games here, considerably fewer than 
the number of bullet games played. This ranges from 35k games to 8 players
who play less than 25 blitz games.

```{r global-effects-17-19-blitz, fig.path = "figures/"}

fit_blitz <- readRDS(here("results/", "Full_Fits", "lichess1700-1900/", 
                    "all_rated_blitz_model.RDS"))

mcmc_hist(fit_blitz$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters 17-19 Blitz",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")

fit_blitz$summary(variables = c("mu1", "mu2", "gamma1", "gamma2"))
```

```{r winner-effects-17-19-blitz, fig.path = "figures/"}
#| fig-height: 9

@@

mcmc_hist(fit_blitz$draws("beta"),
          facet_args = list(labeller = player_labels, ncol = 5)) +
  labs(title = "Player Winner Effects, 17-19 Blitz")

```{r indiv-effects-17-19-blitz, fig.path = "figures/"}
#| fig-height: 9

## indiv effects
names(players) <- paste0("alpha[", 1:length(users), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit_blitz$draws("alpha"),
          facet_args = list(labeller = player_labels, ncol = 5)) +
  labs(title = "Individual Player Effects 17-19 Blitz")
```

@@

Here we have 250k games, ranging from 64k to 16 per player.

```{r global-effects-20-22-blitz, fig.path = "figures/"}
#| fig-height: 9

fit2_blitz <- readRDS(here("results/", "Full_Fits", "lichess2000-2200/", 
                    "all_rated_blitz_model.RDS"))

mcmc_hist(fit2_blitz$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters 20-22 Blitz",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")

fit2_blitz$summary(variables = c("mu1", "mu2", "gamma1", "gamma2"))

```{r winner-effects-20-22-blitz, fig.path= "figures/"}
#| fig-height: 9

## winner effects
players <- users_20_22
names(players) <- paste0("beta[", 1:length(users_20_22), "]")

@@

mcmc_hist(fit2_blitz$draws("beta"),
          facet_args = list(labeller = player_labels, ncol = 5)) +
  labs(title = "Player Winner Effects 20-22 Blitz")

@@

```{r indiv-effects-20-22-blitz, fig.path = "figures/"}
#| fig-height: 9

## indiv effects
names(players) <- paste0("alpha[", 1:length(users_20_22), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit2_blitz$draws("alpha"),
          facet_args = list(labeller = player_labels, ncol = 5)) +
  labs(title = "Individual Player Effects 20-22 Blitz")

Only have limited comparison for these at the moment, so skipped for now.

@@

Here we have only 82k total games, ranging from 15k to 16 games per player.

```{r global-effects-23-25-blitz, fig.path = "figures/"}
#| fig-height: 9

fit3_blitz <- readRDS(here("results/", "Full_Fits", "lichess2300-2500/", 
                    "all_rated_blitz_model.RDS"))

mcmc_hist(fit3_blitz$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters 23-25 Blitz",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")

fit3_blitz$summary(variables = c("mu1", "mu2", "gamma1", "gamma2"))

```{r winner-effects-23-25-blitz, fig.path = "figures/"}
#| fig-height: 9

## winner effects
players <- users_23_25
names(players) <- paste0("beta[", 1:length(users_23_25), "]")

mcmc_hist(fit3_blitz$draws("beta"),
          facet_args = list(labeller = player_labels, ncol = 5)) +
  labs(title = "Player Winner Effects, 23-25 Blitz")

```{r indiv-effects-23-25-blitz, fig.path = "figures/"}
#| fig-height: 9

## indiv effects
names(players) <- paste0("alpha[", 1:length(users_23_25), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit3_blitz$draws("alpha"),
          facet_args = list(labeller = player_labels, ncol = 5)) +
  labs(title = "Individual Player Effects, 23-25 Blitz")

@@

We will only consider this for the bullet games for now.

@@

```{r 17-19-bullet-prev-global, fig.path = "figures/" }

fit_prev <- readRDS(here("results/", "Full_Fits", "lichess1700-1900/", 
                    "all_rated_bullet_model_prev.RDS"))

mcmc_hist(fit_prev$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters, 17-19 Bullet Previous",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")

fit_prev$summary(variables = c("mu1", "mu2", "gamma1", "gamma2"))
```

```{r 17-19-bullet-prev-winner, fig.path= "figures/"}
#| fig-height: 9

@@

mcmc_hist(fit_prev$draws("delta"),
          facet_args = list(labeller = player_labels, ncol = 5)) +
  labs(title = "Player Winner Effects, 17-19 Bullet Previous")
```

```{r 17-19-bullet-prev-indiv, fig.path="figures/"}
#| fig-height: 9

## indiv effects
names(players) <- paste0("alpha[", 1:length(users), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit_prev$draws("alpha"),
          facet_args = list(labeller = player_labels, ncol = 5)) +
  labs(title = "Individual Player Effects, 17-19 Bullet Previous")
```

@@

```{r 20-22-bullet-prev-global, fig.path="figures/"}
fit2_prev <- readRDS(here("results/", "Full_Fits", "lichess2000-2200/", 
                    "all_rated_bullet_model_prev.RDS"))

mcmc_hist(fit2_prev$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters 20-22 Bullet Previous",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")

fit2_prev$summary(variables = c("mu1", "mu2", "gamma1", "gamma2"))
```

```{r 20-22-bullet-prev-winner, fig.path="figures/"}
#| fig-height: 9

@@

mcmc_hist(fit2_prev$draws("delta"),
          facet_args = list(labeller = player_labels, ncol = 5)) +
  labs(title = "Player Winner Effects 20-22 Bullet Previous")
```

```{r 20-22-bullet-prev-indiv, fig.path="figures/"}
#| fig-height: 9

## indiv effects
names(players) <- paste0("alpha[", 1:length(users_20_22), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit2_prev$draws("alpha"),
          facet_args = list(labeller = player_labels, ncol = 5)) +
  labs(title = "Individual Player Effects 20-22 Bullet Previous")
```

@@

```{r 23-25-bullet-prev-global, fig.path="figures/"}
fit3_prev <- readRDS(here("results/", "Full_Fits", "lichess2300-2500/", 
                    "all_rated_bullet_model_prev.RDS"))

mcmc_hist(fit3_prev$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) +
  labs(title = "Global Parameters 23-25 Bullet Previous",
       subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour,
       Gamma2 is ELO Difference")

fit3_prev$summary(variables = c("mu1", "mu2", "gamma1", "gamma2"))
```

```{r 23-25-bullet-prev-winner, fig.path="figures/"}
#| fig-height: 9

@@

mcmc_hist(fit3_prev$draws("delta"),
          facet_args = list(labeller = player_labels, ncol = 5)) +
  labs(title = "Player Winner Effects 23-25 Bullet Previous")

```{r 23-25-bullet-prev-indiv, fig.path="figures/"}
#| fig-height: 9

## indiv effects
names(players) <- paste0("alpha[", 1:length(users_23_25), "]")
player_labels <- as_labeller(players)
mcmc_hist(fit3_prev$draws("alpha"),
          facet_args = list(labeller = player_labels, ncol = 5)) +
  labs(title = "Individual Player Effects 23-25 Bullet Previous")
```

<!-- ### 1700-1900 Blitz -->

<!-- ```{r} -->
<!-- fit <- readRDS(here("results/", "Full_Fits", "lichess1700-1900/",  -->
<!--                     "all_rated_blitz_model_prev.RDS")) -->

<!-- mcmc_hist(fit$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) + -->
<!--   labs(title = "Global Parameters", -->
<!--        subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour, -->
<!--        Gamma2 is ELO Difference") -->

<!-- fit$summary(variables = c("mu1", "mu2", "gamma1", "gamma2")) -->

<!-- ## winner effects -->
<!-- players <- users -->
<!-- names(players) <- paste0("delta[", 1:length(users), "]") -->

<!-- player_labels <- as_labeller(players) -->

<!-- mcmc_hist(fit$draws("delta"), -->
<!--           facet_args = list(labeller = player_labels)) + -->
<!--   labs(title = "Player Winner Effects") -->

<!-- ## indiv effects -->
<!-- names(players) <- paste0("alpha[", 1:length(users), "]") -->
<!-- player_labels <- as_labeller(players) -->
<!-- mcmc_hist(fit$draws("alpha"), -->
<!--           facet_args = list(labeller = player_labels)) + -->
<!--   labs(title = "Individual Player Effects") -->
<!-- ``` -->

<!-- ### 2000-2200 Blitz -->

<!-- ```{r} -->
<!-- fit2 <- readRDS(here("results/", "Full_Fits", "lichess2000-2200/",  -->
<!--                     "all_rated_blitz_model_prev.RDS")) -->

<!-- mcmc_hist(fit2$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) + -->
<!--   labs(title = "Global Parameters", -->
<!--        subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour, -->
<!--        Gamma2 is ELO Difference") -->

<!-- fit2$summary(variables = c("mu1", "mu2", "gamma1", "gamma2")) -->

<!-- ## winner effects -->
<!-- players <- users_20_22 -->
<!-- names(players) <- paste0("delta[", 1:length(users_20_22), "]") -->

<!-- player_labels <- as_labeller(players) -->

<!-- mcmc_hist(fit2$draws("delta"), -->
<!--           facet_args = list(labeller = player_labels)) + -->
<!--   labs(title = "Player Winner Effects") -->

<!-- ## indiv effects -->
<!-- names(players) <- paste0("alpha[", 1:length(users_20_22), "]") -->
<!-- player_labels <- as_labeller(players) -->
<!-- mcmc_hist(fit2$draws("alpha"), -->
<!--           facet_args = list(labeller = player_labels)) + -->
<!--   labs(title = "Individual Player Effects") -->
<!-- ``` -->

<!-- ### 2300-2500 Blitz -->

<!-- ```{r} -->
<!-- fit3 <- readRDS(here("results/", "Full_Fits", "lichess2300-2500/",  -->
<!--                     "all_rated_blitz_model_prev.RDS")) -->

<!-- mcmc_hist(fit3$draws(variables = c("mu1", "mu2", "gamma1", "gamma2"))) + -->
<!--   labs(title = "Global Parameters", -->
<!--        subtitle = "mu1 is Winner Effect, mu2 is Player Effect, Gamma1 is colour, -->
<!--        Gamma2 is ELO Difference") -->

<!-- fit3$summary(variables = c("mu1", "mu2", "gamma1", "gamma2")) -->

<!-- ## winner effects -->
<!-- players <- users_23_25 -->
<!-- names(players) <- paste0("delta[", 1:length(users_23_25), "]") -->

<!-- player_labels <- as_labeller(players) -->

<!-- mcmc_hist(fit3$draws("delta"), -->
<!--           facet_args = list(labeller = player_labels)) + -->
<!--   labs(title = "Player Winner Effects") -->

<!-- ## indiv effects -->
<!-- names(players) <- paste0("alpha[", 1:length(users_23_25), "]") -->
<!-- player_labels <- as_labeller(players) -->
<!-- mcmc_hist(fit3$draws("alpha"), -->
<!--           facet_args = list(labeller = player_labels)) + -->
<!--   labs(title = "Individual Player Effects") -->
<!-- ``` -->

@@

```{r elo-change-23-25-bullet, fig.path = "figures/"}

## load in the data for this

@@

```{r elo-change-17-19-bullet, fig.path= "figures/"}
## look at different bin
path_id <- 1
data_path <- all_data_path[path_id]
files <- list.files(data_path)

@@

bullet_data <- lichess_data %>%
  # filter(Event == "Rated Bullet game") %>%
  # filter(TimeControl == "60+0") %>%
  filter(Variant == "Standard") %>%
  filter(grepl("Rated Bullet game", Event))

users <- unique(bullet_data$Username)

bullet_data %>% 
  mutate(UserELO = ifelse(Username == White, WhiteElo, BlackElo)) %>% 
  group_by(Username) %>% 
  arrange(UTCDate, UTCTime, .by_group = TRUE) %>% 
  select(Username, UTCDate, UTCTime, UserELO) %>% 
  slice(c(1, n()))
```

@@

- Could control for number of games played maybe?

## Change in winner effects across games

- Is there evidence for different winner effects in (say)
the first 1000 games played, vs the last 1000 games played?

## Relationship between winner effects and change in rating/average rating

```{r}
path_id <- 1
data_path <- all_data_path[path_id]
files <- list.files(data_path)

lichess_data <- files %>% 
  map_dfr(~read_player(data_path, .x))
```

<!-- ## Old Questions -->

<!-- Do focal players play each other in this data? -->

<!-- ```{r} -->
<!-- data_path <- here("box_data/lichess1700-1900/") -->

<!-- files <- list.files(data_path) -->
<!-- files <- files[1:25] -->

<!-- read_player <- function(path, file){ -->
<!--   dat <- read_csv(file = paste0(data_path, file), -->
<!--                   col_types = cols(UTCDate = col_date("%Y.%m.%d"), -->
<!--                                    WhiteTitle = col_character(), -->
<!--                                    BlackTitle = col_character(), -->
<!--                                    WhiteElo = col_character(), -->
<!--                                    BlackElo = col_character(), -->
<!--                                    FEN = col_character())) %>%  -->
<!--     select(Username, Event, White, Black, Result, UTCDate, UTCTime,  -->
<!--            WhiteElo, BlackElo, Variant, TimeControl, Termination) %>%  -->
<!--     mutate(WhiteElo = parse_number(if_else(WhiteElo == "?", NA, WhiteElo)), -->
<!--            BlackElo = parse_number(if_else(BlackElo == "?", NA, BlackElo))) -->
<!--   dat -->
<!-- } -->

<!-- lichess_data <- files %>%  -->
<!--   map_dfr(~read_player(data_path, .x)) -->

<!-- users <- unique(lichess_data$Username) -->

<!-- overlap_data <- lichess_data %>%  -->
<!--   filter(White %in% users & Black %in% users) %>%  -->
<!--   filter(Variant == "Standard") %>%  -->
<!--   filter(grepl("Rated Bullet game", Event)) -->

<!-- rm(lichess_data) -->

<!-- overlap_data %>% group_by(Username) %>%  -->
<!--   tally() %>%  -->
<!--   arrange(-n) -->
<!-- ``` -->

<!-- Certain players have a large amount of overlap, looking only at the games we -->
<!-- consider in the analysis. How should these games be accounted for? -->

<!-- ```{r check for 2000-2200 games also} -->
<!-- #| eval: false -->

<!-- ## happens here also, but not as often for this sample -->

<!-- data_path <- here("box_data/lichess2000-2200/") -->

<!-- files <- list.files(data_path) -->
<!-- files <- files[1:10] -->

<!-- read_player <- function(path, file){ -->
<!--   dat <- read_csv(file = paste0(data_path, file), -->
<!--                   col_types = cols(UTCDate = col_date("%Y.%m.%d"), -->
<!--                                    WhiteTitle = col_character(), -->
<!--                                    BlackTitle = col_character(), -->
<!--                                    WhiteElo = col_character(), -->
<!--                                    BlackElo = col_character(), -->
<!--                                    FEN = col_character())) %>%  -->
<!--     select(Username, Event, White, Black, Result, UTCDate, UTCTime,  -->
<!--            WhiteElo, BlackElo, Variant, TimeControl, Termination) %>%  -->
<!--     mutate(WhiteElo = parse_number(if_else(WhiteElo == "?", NA, WhiteElo)), -->
<!--            BlackElo = parse_number(if_else(BlackElo == "?", NA, BlackElo))) -->
<!--   dat -->
<!-- } -->

<!-- lichess_data <- files %>%  -->
<!--   map_dfr(~read_player(data_path, .x)) -->

<!-- users <- unique(lichess_data$Username) -->

<!-- overlap_data <- lichess_data %>%  -->
<!--   filter(White %in% users & Black %in% users) %>%  -->
<!--   filter(Variant == "Standard") %>%  -->
<!--   filter(grepl("Rated Bullet game", Event)) -->

<!-- rm(lichess_data) -->

<!-- overlap_data %>% group_by(Username) %>%  -->
<!--   tally() %>%  -->
<!--   arrange(-n) -->
